---
title: "RegReplacement Lab Data Example"
format: 
   html:
      echo: false
      warning: false
editor: visual
---

```{r}
library(knitr)
library(quarto)
library(psych)

```

# Instance A- 100 data points

```{r}
a = read.table("XYregData.csv",sep = ",",
               header = T)

###Change number of data points here.
RegSubset = a[1:100, ]

ff = lm(Y~X, RegSubset)

```

## Normal linear model

```{r}
plot(jitter(Y)~X, RegSubset)
abline(ff)
```

### Coefficients

```{r}
kable(summary(ff)[4])
```
### Absolute sum of residuals

```{r}
sum(abs(ff$residuals))

```
<br><br>

## Gurobi calculations

### Coefficients

```{r}
ff$coefficients[1] = 8.131478702
ff$coefficients[2] = -0.777281947
plot(jitter(Y)~X, RegSubset)
abline(ff)
kable(t(ff$coefficients))
```
### Absolute sum of residuals

```{r}
GurobiResids = RegSubset$Y-predict(ff,RegSubset)

sum(abs(GurobiResids))

```


# Instance B- 1,000 data points

```{r}
a = read.table("XYregData.csv",sep = ",",
               header = T)

###Change number of data points here.
RegSubset = a[1:1000, ]

ff = lm(Y~X, RegSubset)

```

```{r}
plot(jitter(Y)~X, RegSubset)
abline(ff)
```
## Normal linear model
```{r}
plot(jitter(Y)~X, RegSubset)
abline(ff)
```
### Coefficients

```{r}
kable(summary(ff)[4])
```
### Absolute sum of residuals

```{r}
sum(abs(ff$residuals))

```
<br><br>

## Gurobi calculations

### Coefficients

```{r}
ff$coefficients[1] = 8.131478702
ff$coefficients[2] = -0.777281947
plot(jitter(Y)~X, RegSubset)
abline(ff)
kable(t(ff$coefficients))
```
### Absolute sum of residuals

```{r}
GurobiResids = RegSubset$Y-predict(ff,RegSubset)

sum(abs(GurobiResids))

```


# Instance C- 10,000 data points

```{r}
a = read.table("XYregData.csv",sep = ",",
               header = T)

###Change number of data points here.
RegSubset = a[1:10000, ]

ff = lm(Y~X, RegSubset)

```

## Normal linear model

```{r}
plot(jitter(Y)~X, RegSubset)
abline(ff)
```

### Coefficients

```{r}
kable(summary(ff)[4])
```
### Absolute sum of residuals

```{r}
sum(abs(ff$residuals))

```
<br><br>

## Gurobi calculations

### Coefficients

```{r}
ff$coefficients[1] = 8.131478702
ff$coefficients[2] = -0.777281947
plot(jitter(Y)~X, RegSubset)
abline(ff)
kable(t(ff$coefficients))
```
### Absolute sum of residuals

```{r}
GurobiResids = RegSubset$Y-predict(ff,RegSubset)

sum(abs(GurobiResids))

```

# Instance D- 100,000 data points

```{r}
a = read.table("XYregData.csv",sep = ",",
               header = T)

###Change number of data points here.
RegSubset = a[1:100000, ]

ff = lm(Y~X, RegSubset)

```

## Normal linear model
```{r}
plot(jitter(Y)~X, RegSubset)
abline(ff)
```
### Coefficients

```{r}
kable(summary(ff)[4])
```
### Absolute sum of residuals

```{r}
sum(abs(ff$residuals))

```
<br><br>

## Gurobi calculations

### Coefficients

```{r}
ff$coefficients[1] = 5.156521596
ff$coefficients[2] = -0.50431921
plot(jitter(Y)~X, RegSubset)
abline(ff)
kable(t(ff$coefficients))
```
### Absolute sum of residuals

```{r}
GurobiResids = RegSubset$Y-predict(ff,RegSubset)

sum(abs(GurobiResids))

```
